### 2017-07-11 Bright_Stars/Submission/submission2.tex
update

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=3.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{1.25in}
\fancyfootoffset[L]{1.25in}
\lfoot{\sf PLOS}

@@

%% Misc. Packages
\usepackage{changes}
\definechangesauthor[name={George Chacko}, color=orange]{gc}
\setremarkmarkup{(#2)}

@@

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As proof of principle, we have conducted a case study of five anti-cancer therapeutics \added[id=gc,remark={expanded Abstract to state question of interest}]{to identify the collaborations that resulted in the successful development of these therapeutics as well as nodes of influence in these networks.} We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

@@

 \added[id=gc,remark={clarification of question as per journal request}]{In this study, we document the collaboration networks underlying five FDA-approved therapeutics for cancer. Building upon prior art for single networks we (i) incorporate enhanced data mining methods and network metrics (ii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iii) include information on research awards and peer review of grants (iv) extend single network analysis to map publications and authors across multiple networks. In addition, we identify collaboration across networks and describe the role of funding and peer review outlining a system of layered collaborative activity in scientific discover. By studying additional cures and research advances, we also proceed towards scaling from single case studies to mapping the entire domain of drug development with the expectation that such knowledge will be beneficial in planning, resource allocation and optimization of drug development research. We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.}

@@

\textbf{Analysis}. All data used in this study were acquired exclusively from the sources listed above. \added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}. Computations were performed on infrastructure owned or leased by NET ESolutions, Elsevier, or the Gladstone Institutes. Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}. \added[id=gc,remark={details of new computing procedures}] {The publicly available codes of the Williams study~\cite{bibLotia} were used as the basis for designing the codes used in our study. The previous codes were designed to generate graph objects and make use of graph methods such as breadth-first search (BFS) and depth-first search (DFS for graph traversal. In our approach, we used basic data structures like hash maps, hash sets, lists and aggregations and enriched the data with grants and peer review data. In the Williams study, assembly and analysis of each network took roughly 17 hours per drug, 10 of which are manual processing steps. While our process also involved expert level curation of a foundational set of references for each drug with a cost of roughly 2-5 hours, our network calculations and metrics ran in the order of minutes once the bibliometric data were assembled.} Network visualization was performed using Cytoscape~\cite{bibCytoscape}.

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.99}
{
\begin{subfigure}{.5\textwidth}
  \centering
%  \includegraphics[width=.95\linewidth]{}
  \label{fig:sub1}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
 % \includegraphics[width=.95\linewidth]{}
  \label{fig:sub2}
\end{subfigure}
}
\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.  \emph{Left Panel.} No first generation publications are observed common to all five networks. A single publication is cited in four of five networks. \emph{Right Panel.} 14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
\label{fig: test}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\scalebox{1.3}{
%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\includegraphics[scale=0.1]{proj_percent.png}
\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods). 19,104 unique project numbers were identified as sources of support for publications in all five networks. Of these, 112 projects were common to all five networks. Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research. For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals). A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
\label{fig3}
\end{adjustwidth}
\end{figure}

\textbf{Peer Review} Research support from NIH is typically made through a two stage peer-review process.  The Center for Scientific Review at NIH manages first-stage scientific review of between 50,000-60,000 grant applications each year~\cite{bibBoyack}, a process involving more than 15,000 expert reviewers. In addition, individual Institutes and Centers at NIH manage smaller scale peer review operations. Considering a crude estimate of a 20\% success rate in funding, peer review can be viewed as a collaborative scientific activity and that serves as a selection layer for the upper fifth of applications, thus strongly influencing granting outcomes. To describe this layer at a high-level, we matched the awards in the the five networks to the peer review panels (study sections) that evaluated them for scientific merit and calculated the intersection and union of these peer review panels. Eighty eight unique panel identifiers formed the intersection. Of these, 11 are distinguishable as Special Emphasis Panels that could be either one-time or recurring panels with temporary members, the remaining 77 are chartered panels with relatively stable membership. Some of these panels are no longer active and public records are not easily available to determine their scientific focus. For the 74 panels that could be classified (Supplemental), beyond an obvious focus on cancer, it is evident that the panels represent a rich mix of disciplines such as chemistry, biophysics, genetics, cell biology, and molecular biology; as well as AIDS, pathology, radiology, endocrinology, neurology, mental health, and child health. Four hundred and seven unique panel identifiers formed the union of all five networks. Of these 28 were Special Emphasis Panels, the remaining 379 panels were chartered as in the case of the intersection. These data provide evidence of broad input from invited experts in a collaborative activity that selects promising scientific projects. Assuming an average of 25 reviewers per panel (the number is likely to range from 5-40) and excluding that some of these panels are likely to have met multiple times during the lifespan of the awards in question and that some of these applications for funding may have been reviewed multiple times, a minimum of 10,000 experts comprised this additional layer of scientific influence. We believe that the actual number is likely to be at least double. A more accurate estimate would be possible if historical records of participation in peer review were made publicly available by NIH. We do not have records of awards or peer review from sources other than NIH and this also is a focus of future investigation.

\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We built upon the work of Williams~\cite{bibWilliams} in several ways. Author disambiguation in the their code was not addressed beyond clustering by last name and first names. Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data. We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data. Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our code scales to larger article numbers and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch}, although other data related issues may well emerge.}

While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases. We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness. This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts. These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}). These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science. Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}. The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.

@@

In summary, we have demonstrated a digital methodology based on data mining and network analysis, not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history. Beyond assembling a set of facts about a major scientific advance, it contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research. The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs. \deleted[id=gc,remark={delete in view of previous paragraph}]{such as the Clinical and Translational Science Award (CTSA) Program.} While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science. Overall, no single metric will provide useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be of value.

@@

>>>>

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{change}

@@

% Header and Footer with logo
\usepackage{last,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=3.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{1.25in}
\fancyfootoffset[L]{1.25in}
\lfoot{\sf PLOS}

@@

%% Misc. Packages
\usepackage{changes}
\definechangesauthor[name={George Chacko}, color=orange]{gc}
\setremarkmarkup{(#2)}
\usepackage{listings}

@@

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To document and understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.\added[id=gc,remark={expanded Abstract to state question of interest}]{ Building upon prior art, we have conducted a case study of five anti-cancer therapeutics to identify the collaborations that resulted in the successful development of these therapeutics both within and across their respecive networks.} We have linked the work of over 235,000 authors in roughly 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

@@

 \added[id=gc,remark={clarification of question as per journal request}]{In this study, we document the collaboration networks underlying five FDA-approved therapeutics for cancer. Building upon prior art for single networks we (i) extend single network analysis to map publications and authors across multiple networks (ii) include information on research awards and peer review of grants (iii) include enriched data from a commercially available bibliographic database with disambiguated author identifiers (iv) incorporate modified network metrics and data mining methods. We observe collaboration that extends across networks and describe the role of funding and peer review in sustaining a system of layered collaborative activity in scientific discovery. By studying additional cures and research advances, we also proceed towards scaling from single case studies to mapping the entire domain of drug development with the expectation that such knowledge will be beneficial in planning, resource allocation and optimization of drug development research. We present the results of this case study as a body of work for further study by other researchers, and a step towards mapping the universe of FDA-approved drugs and biologicals.}

@@

\textbf{Analysis}. All data used in this study were acquired exclusively from the sources listed above. \added[id=gc,remark={response to request from editor}]{Data used to generate the figures and tables in this study are available in a Mendeley Data repository~\cite{bibMendeley}}. Computations were performed on infrastructure owned or leased by NETE Solutions, Elsevier, or the Gladstone Institutes. Code and scripts used in this study were written in Java, Python, and R and are archived on a publicly accessible Github repository~\cite{bibGithub}. \added[id=gc,remark={details of new computing procedures}] {The publicly available codes of the Williams study~\cite{bibLotia} were used as the basis for designing the codes used in our study. The previous codes were designed to generate graph objects and make use of graph methods such as breadth-first search (BFS) and depth-first search (DFS for graph traversal. In our approach, we used basic data structures like hash maps, hash sets, lists and aggregations and enriched the first generation set of references with data from Scopus, which indexes more scientific journals~\cite{bibFalagas}, cited references from post-approval literature reviews, cited references from FDA Approval Summaries, direct PubMed searches, grants and peer review data. In the Williams study, assembly and analysis of each network took roughly 17 hours per drug, 10 of which are manual processing steps. While our process also involved expert level curation of a foundational set of references for each drug with a cost of roughly 2-5 hours, our network calculations and metrics ran in the order of minutes once the bibliometric data were assembled.} Network visualization was performed using Cytoscape~\cite{bibCytoscape}.}

@@

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.99}
{
\begin{subfigure}{.5\textwidth}
  \centering
%  \includegraphics[width=.95\linewidth]{}
  \label{fig:sub1}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
 % \includegraphics[width=.95\linewidth]{}
  \label{fig:sub2}
\end{subfigure}
}
\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams.  \emph{Left Panel.} No first generation publications are observed common to all five networks. A single publication is cited in four of five networks. \emph{Right Panel.} 14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
\label{fig: test}
%\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\scalebox{1.3}{
%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
%\end{adjustwidth}
\end{figure}

@@

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\includegraphics[scale=0.1]{proj_percent.png}
\caption{{\bf NIH Research Support} Grant and contract support for publications from NIH in the five networks was identified using ExPORTER data (Materials and Methods). 19,104 unique project numbers were identified as sources of support for publications in all five networks. Of these, 112 projects were common to all five networks. Projects were grouped by mechanism (i) P-  Research Program Projects and Centers (ii) R- Research Projects (iii) M-General Clinical Research Centers Programs (iv) N-Research and Development-Related Contracts (v) U-Cooperative Agreements (vi) T-Training Programs (vii) Z- Intramural Research. For each mechanism, the number of projects in the intersection of all five networks was plotted against the number in the union of all five networks (both expressed as percentages of their respective totals). A higher proportion of Research Program Projects and Centers awards is found in the intersection group.}
\label{fig3}
%\end{adjustwidth}
\end{figure}

\textbf{Peer Review} Research support from NIH is typically made through a two stage peer-review process.  The Center for Scientific Review at NIH manages first-stage scientific review of between 50,000-60,000 grant applications each year~\cite{bibBoyack}, a process involving more than 15,000 expert reviewers. In addition, individual Institutes and Centers at NIH manage smaller scale peer review operations. Considering a crude estimate of a 20\% success rate in funding, peer review can be viewed as a collaborative scientific activity and that serves as a selection layer for the upper fifth of applications, thus strongly influencing granting outcomes. To describe this layer at a high-level, we matched the awards in the the five networks to the peer review panels (study sections) that evaluated them for scientific merit and calculated the intersection and union of these peer review panels. Eighty eight unique panel identifiers formed the intersection. Of these, 11 are distinguishable as Special Emphasis Panels that could be either one-time or recurring panels with temporary members, the remaining 77 are chartered panels with relatively stable membership. Some of these panels are no longer active and public records are not easily available to determine their scientific focus. For the 74 panels that could be classified (Supplemental), beyond an obvious focus on cancer, it is evident that the panels represent a rich mix of disciplines such as chemistry, biophysics, genetics, cell biology, and molecular biology; as well as AIDS, pathology, radiology, endocrinology, neurology, mental health, and child health. Four hundred and seven unique panel identifiers formed the union of all five networks. Of these 28 were Special Emphasis Panels, the remaining 379 panels were chartered as in the case of the intersection. These data provide evidence of broad input from invited experts in a collaborative activity that selects promising scientific projects. Assuming an average of 25 reviewers per panel (the number is likely to range from 5-40) and excluding that some of these panels are likely to have met multiple times during the lifespan of the awards in question and that some of these applications for funding may have been reviewed multiple times, a minimum of 10,000 experts comprised this additional layer of scientific influence. We believe that the actual number is likely to be at least double. A more accurate estimate would be possible if historical records of participation in peer review were made publicly available by NIH. We do not have records of funding awards or peer review from sources other than NIH and this is a focus of future investigation.

\textbf{Network Metrics}  \added[id=gc,remark={revise discussion of methodological advances}]{We have built upon the work of Williams~\cite{bibWilliams} in several ways. Author disambiguation in their code was not addressed beyond clustering by last name and first names. Further, network data were limited to authors, institutions and PMIDs and did not include cited grants and peer review data. We addressed author disambiguation through the use of Scopus authorIDs and enriched the data with grants and peer review data. Whereas, the original code was designed to handle a single drug and was never applied to a problem larger than 5000 articles, our approach scales to over 100,000 articles and our metrics include cross-network calculations.To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as the new nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) is calculated from normalizing the nPIR metric for an researcher to the sum of the researcher's individual PIR scores for each network being studied. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch}, although other data related issues may well emerge.}

While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which in turn depends on data quality in bibliometric databases. We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness. This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts. These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}).  These `bright stars' are elite performers in network(s) of clinical and basic science researchers that reinforce the concept of collaborative translational achievements built upon a body of basic science. Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}. The use of these citation measures will assume greater importance with scale up from small numbers of networks to a greater proportion of the global research network.

@@

In summary, we have demonstrated a digital methodology based on data mining and network analysis, not restricted to  drug discovery and cures alone, that offers burden-reduction in explorations of science history. Beyond assembling a set of facts about a major scientific advance, it contributes to the understanding of collaboration across domains and can be used to  enrich portfolio analysis, planning and optimization, as well as communications of the societal value of research. The approach can be easily adapted to study the collaborative history within and across research portfolios of groups of researchers and targeted programs. \deleted[id=gc,remark={delete in view of previous paragraph}]{such as the Clinical and Translational Science Award (CTSA) Program.} While finer critical evaluation of the content of datasets generated through this approach is best left to experts, the methodology is broadly accessible and can be viewed as another tool for citizen science. Overall, no single metric will provide very useful answers, instead expert interpretation of multiple metrics best matched to curated datasets will be of value.

@@

\bibitem{bibFalagas}
Falagas ME, Pitsouni EI, Malietzis GA, Pappas G.
\newblock{{C}omparison of PubMed, Scopus, Web of Science, and Google Scholar: strengths and weaknesses.}
\newblock FASEB J. 2008 22(2):338-42.
